Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Fix Figure 2 caption
Update result numbers

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/stimuli_shapes.pdf}
    \vspace{0pt}
    \caption{Example stimuli}
    \label{fig:stimuli}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/likelihood_function.pdf}
    \caption{Likelihood function}
    \label{fig:likelihood}
  \end{subfigure}
  \caption{\textbf{Rotated shapes and their similarity.}  \textbf{(a)}
    An example stimulus in which the shapes differ only by a
    rotation. All stimuli consist of five vertices centered around the
    origin, and four edges which create a closed loop from the
    vertices. \textbf{(b)} The approximate likelihood (similarity) of
    $X_b$ given $X_R$, where $X_R$ is a rotation of $X_a$ by the angle
    $R$. The true angle of rotation between $X_a$ and $X_b$ is
    approximately $\frac{\pi}{4}$, corresponding to the global maximum
    in the likelihood function.}
\end{figure}

@@

The correlation between the number of rotations computed by the
na\"ive model and the true angle of rotation was $\rho=-0.11$. The
shape of the data is more interesting (see Figure \ref{fig:rotations},
right panel): the na\"ive model actually corresponds quite well to the
true angle of rotation for $R<\frac{\pi}{2}$ ($\rho=0.63$). This is
unsurprising, because the closer the true angle is to zero, the less
the model has to rotate, and the less likely it will get stuck on
local maxima. Thus, it is more likely to locat the global maximum,
which generally corresponds to the true angle of rotation. For
$R>\frac{\pi}{2}$, we see an increasing tendency to under-rotate
($\rho=-0.42$); this is likely because it finds a local maxima and
ends prematurely.

@@

The rotations computed by the nonparametric model are the most
strongly correlated with the true rotations, albeit negatively so
($\rho=-0.60$). In general, the nonparametric model rotates much more
than should be necessary; this is because the Bayesian quadrature
estimate of $Z$ is too large to accept either hypothesis until a
significant portion of the rotations have been sampled.

>>>>

\begin{figure}[t]
  \centering
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/stimuli_shapes.pdf}
    \vspace{0pt}
    \caption{Example stimuli}
    \label{fig:stimuli}
  \end{subfigure}
  \begin{subfigure}[b]{0.45\textwidth}
    \centering
    \includegraphics[width=\textwidth]{../figures/likelihood_function.pdf}
    \caption{Likelihood function}
    \label{fig:likelihood}
  \end{subfigure}
  \caption{\textbf{Rotated shapes and their similarity.}  \textbf{(a)}
    An example stimulus in which the shapes differ only by a
    rotation. All stimuli consist of five vertices centered around the
    origin, and four edges which create a closed loop from the
    vertices. \textbf{(b)} The approximate likelihood (similarity) of
    $X_b$ given $X_R$, where $X_R$ is a rotation of $X_a$ by the angle
    $R$. The true angle of rotation between $X_a$ and $X_b$ is
    slightly less than $\pi$, corresponding to the global maximum in
    the likelihood function.}
\end{figure}

@@

The correlation between the number of rotations computed by the
na\"ive model and the true angle of rotation was $\rho=-0.11$. The
shape of the data is more interesting (see Figure \ref{fig:rotations},
right panel): the na\"ive model actually corresponds quite well to the
true angle of rotation for $R<\frac{\pi}{2}$ ($\rho=0.64$). This is
unsurprising, because the closer the true angle is to zero, the less
the model has to rotate, and the less likely it will get stuck on
local maxima. Thus, it is more likely to locat the global maximum,
which generally corresponds to the true angle of rotation. For
$R>\frac{\pi}{2}$, we see an increasing tendency to under-rotate
($\rho=-0.42$); this is likely because it finds a local maxima and
ends prematurely.

@@

The rotations computed by the nonparametric model are strongly
correlated with the true rotations ($\rho=0.73$). In general, the
nonparametric model rotates much more than should be necessary; this
is because the Bayesian quadrature estimate of $Z$ is too large to
accept either hypothesis until a significant portion of the rotations
have been sampled.
